Twists of supersymmetric gauge theories

### 2019-08-18 paper.tex
Added a comment on the proof of rotation invariance of the supertranslation action

\begin{proof}
If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

>>>>

\begin{proof}
Let $X$ be an element of $\so(n)$, and write $X \cdot A$ and $X \cdot \lambda$ for the image of the fields $A$ and $\lambda$ under the action of the symmetry $X$.  In particular, we can write
\[I_{\mr{rot}}(A,\lambda, A^\vee, \lambda^\vee, X) = \langle A^\vee, X \cdot A \rangle + \langle \lambda^\vee, X \cdot \lambda \rangle.
\]
Therefore, the operator $\{I_{\mr{rot}}(X), -\}$ on the space of local functionals is freely generated by the operator on linear functionals in the Yang-Mills BV fields given by the action of the rotation $X$.  On the other hand, the Chevalley-Eilenberg differential $\d^{\mr{rot}}_{\mr{CE}}$ is freely generated by the operator on \emph{supertranslations} in $\Sigma$, sending $Q$ to $X \cdot Q$.

So, for the functionals at hand, we compute
\begin{align*}
\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)}(A,\lambda, A^\vee, \lambda^\vee, Q, X),
\end{align*}
and
\begin{align*}
\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2, X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}(\lambda^\vee, Q_1, Q_2, X).
\end{align*}
\chris{I should take care that the signs I introduce when I move $X$ around are all correct here, and include more explanation.  This argument assumes that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$, that $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$, which I think should follow from $\so(n)$ equivariance of $\Gamma$ and $\rho$, but I should check and verify the signs.}
\end{proof}
